Benchmarking on Rigetti architecture

### 2022-09-29 txt/manuscript.tex
Rewrite section 2.2.1.

\subsubsection{Model specification}
Theoretically, the scenario of this set-up assumes that Alice and Bob have an 
unknown measurement device, a black--box. Alice has hidden one of the two 
measurements, say $\SS$ and $\TT$,  in the black box. Bob only has information that it 
performs one of such measurements. 
They want to know the upper bound of the   probability of correct discrimination between $\SS$ and $\TT$ and construct the optimal discrimination strategy between them to achieve the highest possible probability of discrimination. 
Theoretical results of discrimination of 
von Neumann measurements are well-known and characterized 
in~\cite{puchala2018strategies}.

In this work we will consider the problem of discrimination between von Neumann measurement in the computational basis  and  the von Neumann measurement in basis $U$, where $U$ is a unitary matrix. 
This scheme is 
presented in Fig.~\ref{fig:theoretical_scheme} and 
can be divided into the following steps:

@@

@@

\begin{enumerate}\item Alice and Bob share entanglement state $\ket{\psi_{AB}}$.
	\item Alice performs one of two known measurements,  say $\PP_{\Id}$ and $\PP_{U}$,  on part $A$ of the input 
	state  $\ket{\psi_{AB}}$.
	\item Alice   performs the conditional binary measurement on the part 
	$B$ based on
	the output label $i$. 
	\item  Bob measures the part $B$ of the input state  $\ket{\psi_{AB}}$ and 
	makes a decision based on received label $j$. If $j=0$, he decides that the measurement $\PP_U$ is hidden in the black box. Otherwise, he decides that the measurement $\PP_{\Id}$ was hidden in the black box. 
\end{enumerate}

>>>>

\subsubsection{Model specification}
The scenario assumes that Alice and Bob have access to an unknown measurement
device, a black box. Alice has hidden one of the two measurements, either $\SS$
or $\TT$, in the black box. Bob only has the information that the black box
performs one of these measurements. They want to know the upper bound on the
probability of correct discrimination between $\SS$ and $\TT$. They also want to
construct the optimal discrimination strategy to achieve the highest probability
of correct discrimination. Theoretical results on discrimination of von Neumann
measurements are characterized in~\cite{puchala2018strategies}.

In this work we will consider the problem of discrimination between von Neumann 
measurement in the computational basis and a von Neumann measurement in basis 
$U$, where $U$ is a unitary matrix. 
The scheme of discrimination can be divided into the following steps, which are 
illustrated in Fig.~\ref{fig:theoretical_scheme}.

@@

\begin{enumerate}
	\item Alice and Bob share an entangled state $\ket{\psi_{AB}}$ on registers 
	$A$ and $B$.
	\item Alice performs one of two known measurements (either $\PP_{\Id}$ or 
	$\PP_{U}$) on part $A$ of the input state  $\ket{\psi_{AB}}$.
	\item Alice performs the conditional binary measurement on the part 
	$B$ based on the output label $i$. 
	\item  Bob measures part $B$ of the input state  $\ket{\psi_{AB}}$ and 
	makes a decision based on the received label $j$. If $j=0$, then he decides 
	that the the black box contains $\PP_U$. Otherwise, he decides that the 
	black box contains $\PP_{\Id}$. 
\end{enumerate}

@@
